### 2014-03-26 ms_probaweb.tex
Bibtex file for Tim

\bibliography{library}

@@

The niche concept is central in biogeography to understand and predict species
distribution. Several attempts have been made to refresh the concept, but its
main usage still follows Hutchinson’s idea that species interactions restrict
the fundamental niche to a realized one. Despite its intuitive
interpretation and translation into species distribution models, the 
concept has been constantly criticized (Hardin, 1960; Peters, 1991;
Chase2003; Silvertown, 2004; Soberon, 2007) and several attempts have
been made to expand and reinforce it.

>>>>

\bibliography{library, tim}

@@

The niche concept is key to understand and predict species
distribution. Several attempts have been made to refresh it, but its main
usage still follows Hutchinson’s idea that species interactions restrict
the fundamental niche to a realized one \parencite{Blonder2014}. Despite its
intuitive interpretation and translation into species distribution models,
the concept has been constantly criticized (Hardin, 1960; Peters, 1991;
Chase2003; Silvertown, 2004; Soberon, 2007) and several attempts have been
made to expand and reinforce it.
